An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-23 VLDB2026/main.tex
change

				Audio & 192 & 53,387 & 200 & 14& Audio& AF \\
				Deep & 96 & 1,000,000 & 10,000 & 22& Image& RF \\
				Enron & 1369 & 94,987 & 200 & 23& Text& AF \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image& AF \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text& AF \\
				Msong & 420 & 992,272 & 200 & 23& Audio& AF \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image& AF \\

				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image \\
				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
				\bottomrule
			\end{tabular}
		}
	\end{table}

>>>>

				Audio & 192 & 53,387 & 200 & 14& Audio& AF \\
				Enron & 1369 & 94,987 & 200 & 23& Text& AF \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image& AF \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text& AF \\
				Msong & 420 & 992,272 & 200 & 23& Audio& AF \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image& AF \\

				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				Deep1M & 96 & 1,000,000 & 10,000 & 22 & Image& RF \\
				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio& Both \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image& Both \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image& Both \\
				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image& Both \\
				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image& Both \\
				\bottomrule
			\end{tabular}
		}
	\end{table}
